Shades of Green in the Swedish Forest-Based Bioeconomy Transition

### 2024-01-29 docs/reports/paper/paper1.qmd
Refactor SQL query to exclude non-forest innovation

bioeconomy = pd.read_sql(
    """
select
  i.sinno_id,
  i.innovation_name_in_swedish AS name,
  i.description_in_swedish AS description,
  i.additional_information_if_origin_new_scientific_discovery || i.additional_information_if_origin_new_technologies_or_materials || i.additional_info_if_origin_official_regulation_legislation_and_standards || i.additional_information_if_origin_solution_for_a_problem || i.additional_information_if_origin_performance || i.additional_information_if_origin_other AS info,
  i.year_of_commercialization AS year,
  us.use_sector
from
  innovation i
  join use_sectors us on i.sinno_id = us.sinno_id
where
  (
    us.use_sector like '02%'
    or us.use_sector like '20%'
    or us.use_sector like '21%'
    or us.use_sector like '36%'
    or product_code like '02%'
    or product_code like '20%'
    or product_code like '21%'
    or product_code like '36%'
  )
  or (
    description like '%virke%'
    or description like '%cellulos%'
    or description like '%lignin%'
    or description like '%spån%'
    or description like '%bark%'
    or description like '%levulinsyra%'
    or description like '%furfural%'
    or description like '%svarttjära%'
    or description like '%svartlut%'
    or description like '%växtbas%'
    or description like '%ved%'
    or description like '%trä%'
    or description like '%skog%'
    or description like '%biobränsle%'
    or description like '%biologisk%'
    or description like '%nedbrytbar%'
    or description like '%papper%'
    or description like '%pappret%'
    or description like '%karton%'
    or description like '%tencel%'
  );
""",
    conn,
)

>>>>

bioeconomy = pd.read_sql(
    """ 
    SELECT distinct sinno_id from (SELECT
    i.sinno_id,
    i.innovation_name_in_swedish AS name,
    i.literal_name_of_innovating_firm_sinnos_common_name_sinno_id AS firm,
    i.literal_name_of_collaborator_sinnos_common_name_sinno_id AS collaborator_0,
    i.literal_name_of_collaborator_sinnos_common_name_sinno_id1 AS collaborator_1,
    i.literal_name_of_collaborator_sinnos_common_name_sinno_id2 AS collaborator_2,
    i.literal_name_of_collaborator_sinnos_common_name_sinno_id3 AS collaborator_3,
    i.literal_name_of_collaborator_sinnos_common_name_sinno_id4 AS collaborator_4,
    i.literal_name_of_collaborator_sinnos_common_name_sinno_id5 AS collaborator_5,
    i.literal_name_of_collaborator_sinnos_common_name_sinno_id6 AS collaborator_6,
    i.literal_name_of_collaborator_sinnos_common_name_sinno_id7 AS collaborator_7,
    i.literal_name_of_collaborator_sinnos_common_name_sinno_id8 AS collaborator_8,
    i.description_in_swedish AS description,
    i.year_of_commercialization AS year,
    us.use_sector
    FROM
    innovation i
    JOIN use_sectors us ON i.sinno_id = us.sinno_id
    WHERE
    (
        us.use_sector LIKE '02%'
        OR us.use_sector LIKE '20%'
        OR us.use_sector LIKE '21%'
        OR us.use_sector LIKE '36%'
        OR product_code LIKE '02%'
        OR product_code LIKE '20%'
        OR product_code LIKE '21%'
        OR product_code LIKE '36%'
    )
    OR (
        description LIKE '%virke%'
        OR description LIKE '%cellulos%'
        OR description LIKE '%lignin%'
        OR description LIKE '%spån%'
        OR description LIKE '%bark%'
        OR description LIKE '%levulinsyra%'
        OR description LIKE '%furfural%'
        OR description LIKE '%svarttjära%'
        OR description LIKE '%svartlut%'
        OR description LIKE '%växtbas%'
        OR description LIKE '%ved%'
        OR description LIKE '%trä%'
        OR description LIKE '%skog%'
        OR description LIKE '%biobränsle%'
        OR description LIKE '%biologisk%'
        OR description LIKE '%nedbrytbar%'
        OR description LIKE '%papper%'
        OR description LIKE '%pappret%'
        OR description LIKE '%karton%'
        OR description LIKE '%tencel%'
    )
    AND i.sinno_id not in (select sinno_id from categorization_notes
    where notes not like "%not forest%"));
""",
    conn,
)
